\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\usepackage{float}
\usepackage{hyperref}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\usepackage{listings}
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}
\lstset{style=mystyle}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}

\title{Problem Set 3}
\date{Due: November 20, 2022}
\author{Applied Stats/Quant Methods 1}


\begin{document}
	\maketitle
	\section*{Instructions}
	\begin{itemize}
		\item Please show your work! You may lose points by simply writing in the answer. If the problem requires you to execute commands in \texttt{R}, please include the code you used to get your answers. Please also include the \texttt{.R} file that contains your code. If you are not sure if work needs to be shown for a particular problem, please ask.
		\item Your homework should be submitted electronically on GitHub.
		\item This problem set is due before 23:59 on Sunday November 20, 2022. No late assignments will be accepted.
		\item Total available points for this homework is 80.
	\end{itemize}
	
	\vspace{.25cm}
	
	\noindent In this problem set, you will run several regressions and create an add variable plot (see the lecture slides) in \texttt{R} using the \texttt{incumbents\_subset.csv} dataset. Include all of your code.
	
	\vspace{.5cm}
	\section*{Question 1}
	\vspace{.25cm}
	\noindent We are interested in knowing how the difference in campaign spending between incumbent and challenger affects the incumbent's vote share. 
	\begin{enumerate}
		\item Run a regression where the outcome variable is \texttt{voteshare} and the explanatory variable is \texttt{difflog}. 	\vspace{5cm} 
		
		$model1 <- lm(formula = voteshare ~ difflog, data = incumbents)$
		
		\item Make a scatterplot of the two variables and add the regression line. 	\vspace{7cm} 
		
		$firstgraph <- incumbents %>%
		ggplot(aes(x=difflog, y=voteshare)) +
		geom_point(alpha=0.2) +
		labs(x="Difference in campaign spending",
		y="Incumbent voteshare") +
		geom_smooth()$
	
		\item Save the residuals of the model in a separate object.	\vspace{7cm} 
		
		$res1 <- residuals(model1)$
		\item Write the prediction equation.
		Y = 0.579031 + 0.041666 + e
	\end{enumerate}
	
	\newpage
	
	\section*{Question 2}
	\noindent We are interested in knowing how the difference between incumbent and challenger's spending and the vote share of the presidential candidate of the incumbent's party are related.	\vspace{.25cm}
	\begin{enumerate}
		\item Run a regression where the outcome variable is \texttt{presvote} and the explanatory variable is \texttt{difflog}.	\vspace{5cm} 
		
		$model2 <- lm(formula= presvote ~ difflog, data = incumbents)$
		\item Make a scatterplot of the two variables and add the regression line. 	\vspace{5cm}
		
		$secondgraph <- incumbents %>%
		ggplot(aes(x=difflog, y=presvote)) +
		geom_point(alpha=0.2) +
		labs(x="Difference in campaign spending",
		y="Voteshare of incumbent party presidential candidate") +
		geom_smooth()$
		\item Save the residuals of the model in a separate object.	\vspace{5cm}
		
		$res2 <- residuals(model2)$
		\item Write the prediction equation.
		Y = 0.507583 + 0.023837 + e
	\end{enumerate}
	
	\newpage	
	\section*{Question 3}
	
	\noindent We are interested in knowing how the vote share of the presidential candidate of the incumbent's party is associated with the incumbent's electoral success.
	\vspace{.25cm}
	\begin{enumerate}
		\item Run a regression where the outcome variable is \texttt{voteshare} and the explanatory variable is \texttt{presvote}.
		\vspace{5cm}
		
		$model3 <- lm(formula = voteshare ~ presvote, data = incumbents)$
		\item Make a scatterplot of the two variables and add the regression line.
		
		$thirdgraph <- incumbents %>%
		ggplot(aes(x=presvote, y=voteshare)) +
		geom_point(alpha=0.2) +
		labs(x="Voteshare of incumbent party presidential candidate",
		y="Incumbent voteshare") +
		geom_smooth()$ 
		\vspace{5cm}
		\item Write the prediction equation.
		Y = 0.441330 + 0.388018 + e
	\end{enumerate}
	
	
	\newpage	
	\section*{Question 4}
	\noindent The residuals from part (a) tell us how much of the variation in \texttt{voteshare} is $not$ explained by the difference in spending between incumbent and challenger. The residuals in part (b) tell us how much of the variation in \texttt{presvote} is $not$ explained by the difference in spending between incumbent and challenger in the district.
	\begin{enumerate}
		\item Run a regression where the outcome variable is the residuals from Question 1 and the explanatory variable is the residuals from Question 2.	\vspace{6cm}
		
		$residuals <- data.frame(res1, res2)$
		
		$reg_res <- lm(formula = res1~res2, data=residuals)$
		\item 
		Make a scatterplot of the two residuals and add the regression line. 	\vspace{6cm}
		
		$fourthgraph <- residuals %>%
		ggplot(aes(x=res2, y=res1)) +
		geom_point(alpha=0.2) +
		labs(x="Residuals of second regression",
		y="Residuals of first regression") +
		geom_smooth()$
		\item Write the prediction equation.
		Y = -4.860e-18 + 2.569e-01 + e
	\end{enumerate}
	
	\newpage	
	
	\section*{Question 5}
	\noindent What if the incumbent's vote share is affected by both the president's popularity and the difference in spending between incumbent and challenger? 
	\begin{enumerate}
		\item Run a regression where the outcome variable is the incumbent's \texttt{voteshare} and the explanatory variables are \texttt{difflog} and \texttt{presvote}.	\vspace{5cm}
		
		$model4 <- lm(formula = voteshare ~ difflog + presvote, 
		data=incumbents)$
		\item Write the prediction equation.	\vspace{5cm}
		 
		 Y = 0.4486442 + 0.0355431 + 0.2568770 + e
		\item What is it in this output that is identical to the output in Question 4? Why do you think this is the case?
		
		$The intercepts for the residual regression and presvote~voteshare.$
	\end{enumerate}
	
	
	
	
\end{document}